RDF Validation of Metadata \\ on Person-Level and Aggregated Data

### 2015-03-03 paper/paper7/paper7.tex
4.2

\textbf{Frequencies and Descriptive Statistics.}
Percentage values are valid when they are between 0 and 100.
The constraint type \emph{literal ranges} (\emph{R-45}) restricts data property ranges [$V_{min}$,$V_{max}$] within the context of given classes.
A constraint of this type applies to the property \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set ($\mathcal{SL}_{2}$).

{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable} must exactly be 100.

>>>>

\textbf{Frequencies and Descriptive Statistics.}
Percentage values are valid when they are between 0 and 100.
The constraint type \emph{literal ranges} (\emph{R-45}) restricts data property ranges [$V_{min}$,$V_{max}$] within the context of given classes.
A constraint of this type applies to the property \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set ($\mathcal{SL}_{2}$).
{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}) of a variable code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), e.g., must exactly be 100 ($\mathcal{SL}_{2}$).
